MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-24 paper.Rmd
Better footnote.

Input data for the PFU Database can be found in @Marshall:2023aa.
Access to the PFU Database can be obtained via correspondence 
with author [PEB](mailto:P.E.Brockway@leeds.ac.uk)^[Access to the PFU Database
is restricted to those who have access to [IEA WEEB data][link-ieaweeb].].

>>>>

Input data for the PFU Database can be found in @Marshall:2023aa.
Access to the PFU Database can be obtained via correspondence 
with author [PEB](mailto:P.E.Brockway@leeds.ac.uk)^[Because the PFU Database contains
primary and final energy [IEA WEEB][link-ieaweeb] data, 
access to the PFU Database
is restricted to those who have access to [IEA WEEB][link-ieaweeb] data.].
